Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
align
render doc

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
    github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   #bookdown::word_document2:
    #reference_docx: template.docx
bibliography: ../references/swim.bib
#csl: csl.csl
---

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only `r n10` of these 12 individuals had more than 10 swimming
events, suggesting that for ~10% of narjed individuals swimming is relatively
common, on average occurring approximately every `r indMean` days during
ice-free seasons. We did not detect any swimming events for the remaining 17
individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare for most caribou. Overall, there appears to be three
groups of individuals: those that swim often (n = 3, every ~`r indMean` days), those that
swim occasionally (n = 9, every ~`r ind2Mean` days), and those that never swam (n = 17). We are also
unable to draw conclusions about the prevalence of swimming in the ocean by male
caribou: our initial visual observation was of an adult male, but our GPS data
only included females.

@@

<!--![**Figure 2**: Map of the Fogo Island archipelago. Fogo Island is the largest
island in the archipelago (237.71 km^2^), but there are at least three other
large islands: Western Indian (77.6 km^2^), Eastern Indian (38.7 km^2^) and
Change (XX km^2^) Islands, as well as numerous smaller islands, including
Blundon’s (1.18 km^2^), North Long (1.01 km^2^), South Long (0.48 km^2^), Kate’s
(1.64 km^2^), and Brother’s (1.59 km^2^) Islands. Habitats are similar across
the archipelago, consisting largely of coniferous and mixed forests of balsam
fir (*Abies balsamea*), black spruce (*Picea mariana*), and white birch 
(*Betula papyrifera*) as well as bogs, lakes, lichen and rocky
barrens.]()<!--(../graphics/IMG_1562.JPG)-->

>>>>

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/swim.bib
#csl: csl.csl
---

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. Only `r n10` of these 12 individuals had more than 10 swimming
events, suggesting that for ~10% of narjed individuals swimming is relatively
common, on average occurring approximately every `r indMean` days during
ice-free seasons. We did not detect any swimming events for the remaining 17
individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare for most caribou. Overall, there appears to be three
groups of individuals: those that swim often (n = 3, every ~`r indMean` days), those that
swim occasionally (n = 9, every ~`r ind2Mean` days), and those that never swam (n = 17). We are also
unable to draw conclusions about the prevalence of swimming in the ocean by male
caribou: our initial visual observation was of an adult male, but our GPS data
only included females.

@@

![**Figure 2**: Map of the Fogo Island archipelago. Fogo Island is the largest
island in the archipelago (237.71 km^2^), but there are at least three other
large islands: Western Indian (77.6 km^2^), Eastern Indian (38.7 km^2^) and
Change (XX km^2^) Islands, as well as numerous smaller islands, including
Blundon’s (1.18 km^2^), North Long (1.01 km^2^), South Long (0.48 km^2^), Kate’s
(1.64 km^2^), and Brother’s (1.59 km^2^) Islands. Habitats are similar across
the archipelago, consisting largely of coniferous and mixed forests of balsam
fir (*Abies balsamea*), black spruce (*Picea mariana*), and white birch 
(*Betula papyrifera*) as well as bogs, lakes, lichen and rocky
barrens.](../graphics/Fig2.png)
<!-- edit caption -->
